### 2020-04-27 chemev/MWbimodality/synopsis1/synopsis.tex
plots: density map of lintexp models ; synopsis: minor updates

\begin{figure*}[!h] 
\centering 
\includegraphics[scale = 0.3]{../plots/rgal_birth/hayden2015plot/moddisk_vigorousSF.png} 
\caption{Each panel corresponds to a bin in galactocentric radius 
$R_\text{gal}$ (denoted at the top of each column) and height above/below the 
plane $\left|z\right|$ (denoted in the middle panel of each column). Points 
are color-coded according to the $R_\text{gal}$ at which each star was born, 
and their size scales linearly with their mass. There is a bimodality most 
apparent in the $R_\text{gal}$ = 5 - 7 kpc bin, in agreement with 
observations.} 
\end{figure*}

\begin{figure*}[!h] 
\centering 
\includegraphics[scale = 0.3]{../plots/age/hayden2015plot/moddisk_vigorousSF.png}
\caption{
Same as above, but points are color-coded by age in Gyr. Of particular 
interest is the population of young (age $\lesssim$ 1 Gyr) stars with mild 
$\alpha$-enhancements seen in many of these panels; this suggests that a 
population of young $\alpha$-rich stars is a natural consequence of radial 
migration. 
} 
\end{figure*}

@@

>>>>

\begin{figure*}[!h] 
\centering 
\includegraphics[scale = 0.3]{../plots/rgal_birth/hayden2015plot/moddisk_vigorousSF.png} 
\caption{Each panel corresponds to a bin in galactocentric radius 
$R_\text{gal}$ (denoted at the top of each column) and height above/below the 
plane $\left|z\right|$ (denoted in the middle panel of each column). Points 
are color-coded according to the $R_\text{gal}$ at which each star was born, 
and their size scales linearly with their mass. There is a bimodality most 
apparent in the $R_\text{gal}$ = 5 - 7 kpc bin, in agreement with 
observations.} 
\label{fig:rgal_birth:hayden2015plot:moddisk_vigorousSF} 
\end{figure*}

\begin{figure*}[!h] 
\centering 
\includegraphics[scale = 0.3]{../plots/age/hayden2015plot/moddisk_vigorousSF.png}
\caption{
Same as above, but points are color-coded by age in Gyr. Of particular 
interest is the population of young (age $\lesssim$ 1 Gyr) stars with mild 
$\alpha$-enhancements seen in many of these panels; this suggests that a 
population of young $\alpha$-rich stars is a natural consequence of radial 
migration. 
} 
\label{fig:age:hayden2015plot:moddisk_vigorousSF} 
\end{figure*}

@@

\begin{figure*} 
\centering 
\includegraphics[scale = 0.3]{../plots/stellarMDFS/hayden2015plot/moddisk_vigorousSF.png} 
\caption{
Probability distribution functions of stars in [O/Fe] in bins of [Fe/H], 
present-day galactocentric radius $R_\text{gal}$, and present-day height 
above/below the plane $\left|z\right|$. Rows correspond to bins in 
$\left|z\right|$ as noted in the middle-right column. Columns correspond to 
bins in $R_\text{gal}$ as noted at the top of each column. Different colors 
denote different bins in metallicity as noted by the legend in the right-hand 
column. There is a bimodality most apparent in the 5-7 kpc and 7-9 kpc bins; 
the high-$\alpha$ population is most pronounced at low $R_\text{gal}$ and 
high $\left|z\right|$, and the opposite for the low-$\alpha$ population, 
in qualitative agreement with observational results. 
}
\end{figure*}

\begin{figure*} 
\centering 
\includegraphics[scale = 0.3]{../plots/rgal_birth/hayden2015plot/iodisk_reference.png} 
\caption{
Same as figure~\ref{fig:rgal_birth:hayden2015plot:moddisk_vigorousSF}, but for 
an inside-out formation model in which each annulus has an exponential infall 
history and an initial gas supply of 0. 
}
\end{figure*}

\begin{figure*} 
\centering 
\includegraphics[scale = 0.3]{../plots/age/hayden2015plot/iodisk_reference.png} 
\caption{Same as figure~\ref{fig:age:hayden2015plot:moddisk_vigorousSF}, but 
for an inside-out formation model in which each annulus has an exponential 
infall history and an initial gas supply of 0. }
\end{figure*}
